---
title: "`r params$report_name` Break-Up Report `r lubridate::year(Sys.Date())`"
subtitle: " <br><br>"
date: "Prepared on `r Sys.Date()`"
output: 
  word_document:
      reference_docx: style_template.docx
      toc: true
      toc_depth: 2
params:
  stations: stations
  report_name: report_name
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyhydat)
library(tidyhydat.ws)
source("../Hydrometric_Level_mASL.R")
source("../Hydrometric_Flow.R")
```

\newpage

This report is generated by the Yukon Government based on data pulled from the [Real-Time Hydrometric Data](https://wateroffice.ec.gc.ca/mainmenu/real_time_data_index_e.html) published by the Government of Canada. This report is based on data downloaded at `r .POSIXct(Sys.time(), tz="America/Whitehorse")` Yukon time.


# Current Status and Observations

[Enter update here]

\newpage

# Station data

Water level and flow data is listed below in order of historical relative importance to flooding.

In the future, the order of listing could depend instead on which stations is highest in relation to historical levels.

```{r all stations, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6.5, results='asis'}

for(i in stations) {
  tryCatch ( {
    station_info <- tidyhydat::hy_stations(i)
    levelData <- level_data(
    station_number = i,
    extract_realtime = TRUE,
    select_years = lubridate::year(Sys.Date())
  )
    startYear <- min(lubridate::year(levelData[[1]]$Date), na.rm = T)
    today <- levelData[[3]]$Value[levelData[[3]]$Date==Sys.Date()]
    todayPerc <- round(levelData[[3]]$prctile[levelData[[3]]$Date==Sys.Date()],2)
    yesterday <- levelData[[3]]$Value[levelData[[3]]$Date==(Sys.Date()-1)]
  
    cat(" \n## ", tidyhydat::hy_stations(i)$STATION_NAME," (Station ", i, ")  \n")
    cat("### Level plot")
  
    cat("  \n The current level is ", round(today,3)," meters above sea level which corresponds to the ", todayPerc, " percentile of historic levels for this station. Since yesterday, the level has ", ifelse(today<yesterday, "decreased", "increased"), "by ", round(abs(today-yesterday), 3)," meters.  \n")
  
    levelPlot <- level_plot(
      station_number = i,
      complete_year = levelData[[2]],
      plot_years_df = levelData[[3]],
      dummy_year_df = levelData[[4]],
    )
    print(levelPlot)
  
    cat("  \n This station is located in ", station_info$PROV_TERR_STATE_LOC, " at longitude ", round(station_info$LONGITUDE, 2), ", latitude ", round(station_info$LATITUDE,2), ". Data collection began in ", startYear, " and the historic data are ", spatstat.utils::percentage(sum(stats::complete.cases(levelData[[1]]))/nrow(levelData[[1]])), " complete.  \n")
    cat("\n\n\\pagebreak\n")
  }, error = function(e) {})
}
```

# Weather Forecast and Products

```{r}

```

# Still Images

```{r}

```

## Other images

```{r}

```
